---
title: "STAT 184 Homework Exercises"
author: "zhiyaun zhang"
subtitle: DataComputing Chapters 7
output:
  html_document:
    df_print: paged
---

###question 7.1
##1 reduction
##2 reduction
##3 reduction
##4 transformation
##5 neither
##6 reduction
##7 could determine by using reduction function
##8 reduction

###question7.3
##1 200 cases
##2 BETSYHODGES DONSAMUELS MARKANDREW JACKYCHERRYHOMES bobfine/camwinton
##3 first#834  second#10598 third#19210
##4 BETSYHODGES DONSAMUELS MARKANDREW
##5 B   ETSYHODGE
```{r}
rm(list = ls())

library(tidyverse)
library(mosaic)
library(mosaicData)
library(dcData)

data("Minneapolis2013", package = "dcData")
Minneapolis2013 %>% 
  summarise(count = n())
Minneapolis2013 %>% 
    group_by(Second) %>%
    summarise(count = n()) %>%
    arrange(desc(count)) %>%
    head(5)
Minneapolis2013 %>% 
    group_by(First) %>%
    summarise(count = n()) %>%
    filter(First == "undervote")
Minneapolis2013 %>% 
    group_by(Second) %>%
    summarise(count = n()) %>%
    filter(Second == "undervote")
Minneapolis2013 %>% 
    group_by(Third) %>%
    summarise(count = n()) %>%
    filter(Third == "undervote")
Minneapolis2013 %>% 
    group_by(First, Second) %>%
    summarise(count = n()) %>%
    arrange(desc(count)) %>%
    head(3)
Minneapolis2013 %>% 
    group_by(Precinct) %>%
    summarise(count = n()) %>%
    arrange(desc(count)) %>%
    head(1)
```

### Question7.5
##1 this uis the data that acounts for first and second group combination
##2 this is the case that counts for totol cases for each voters
##3 this is the cases tha counts for total cases for first and second voters' combination
##4 this is the total cases for the voters group by the first and second vote
```{r}
VoterData_A <-
  Minneapolis2013 %>%
  group_by(First, Second)

head(VoterData_A)
VoterData_B <-
  Minneapolis2013 %>%
  summarise(total = n())

VoterData_B
VoterData_C <-
  Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise(total = n())
VoterData_C
```

###question6
```{r}
data("ZipGeography")

LandPop <- ZipGeography %>%
  group_by(State) %>% 
  summarise(POPSUM = sum(Population, na.rm = TRUE), 
            LandSUM = sum(LandArea, na.rm = TRUE),
            POPperLandSUM = sum(Population, na.rm = TRUE)/sum(LandArea, na.rm = TRUE))

# make scatter plot showing relationship (used interactive command like `mplot(LandPop)`)
ggplot(data = LandPop,
       aes(x = LandSUM, 
           y = POPSUM)) + 
  geom_point() + 
  aes(colour = State) 
LandPop %>%
  mUSMap(key = "State", fill = "POPSUM")
LandPop %>%
  mUSMap(key = "State", fill = "POPperLandSUM")
```
###question7.7
##a  gives the data about mean and number of the data which filtered by sex
##b gives the data about mean  and number of the data which filtered by diagnosis
##c gives the data about mean  and number of the data which filtered by sex and diagnosis combination
##d gives the data about mean  and number of the data which filtered by diagnosis and age combination
##e gives the data about mean  and number of the data which filtered by age


###question 7.8
```{r}
data("ZipDemography", package = "dcData")

ggplot(ZipDemography, 
       aes(x = Foreignborn, y = SpeakalanguageotherthanEnglishathome5yearsandover)) +
  geom_point()



```