---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

##
```{r}
library(mosaic)
library(dcData)
library(tidyverse)
```

###15.1
```{r}
data("CPS85")
ggplot(CPS85,aes(sex,wage,fill=sex))+geom_boxplot()

```

###15.2
```{r}
data("NCHS")
```
##based on the graph, I would conclude that most likely height among NCHS at around 1.65 meter
##baesd on the 2nd graph, most likely for men is around 1.7 meter, for women is around 1.6 ##meter
##based on the thrid graph, for 40 years old will be around 26 bmi, for 70 years old will be around 27.5 bmi

###15.3
```{r}
ggplot(CPS85,aes(educ, wage,colour=sex))+geom_point()+stat_smooth(method = lm)+ylim(0,15)
```
###15.4
```{r}
data("Galton")
ggplot(Galton, aes(height,mother))+geom_density_2d()+facet_wrap(~sex)

```
###15.5
## statistically I would not conclude that there is any linear trend. Althought there is a line. so no
##I would conclude that there is half of points over the confidence interval, so there is no relationships
## I think it consistent with the data
## 2times 
## yes_