---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
## question 1
## variables are living area, bathrooms, bedrooms, fireplaces
## no
## 28372.15
## also depends on number of fireplaces, living area, number of bathroom and bedrooms

library(mosaic)
library(dcData)
library(party)
data("NCHS")
```

```{r}
NCHS %>%
  na.omit() %>%
  nrow()
CompleteCases <- 
  NCHS %>%
  select(diabetic, weight, age, bmi, chol, smoker) %>%
  na.omit() 
CompleteCases %>% nrow()

mod2 <- party::ctree(diabetic ~ weight + bmi + age, data = CompleteCases)

plot(mod2, type = "simple")
CompleteCases %>%
  mutate(probability = as.numeric(predict(mod2)), 
         likelihood = ifelse(diabetic, probability, 1-probability)) %>%
  summarise(log_likelihood = sum(log(likelihood)))
```




## A useful risk factor splits the population into groups with very high and with very low probabilities of diabetes. For instance, node 25 marks a group with a 31.9% risk of diabetes. This result is larger than other groups which indicates that bmi greater than 35,34 is associated with higher risk of diabetes

## node 5 suggests that about 0.002% of persons in the NCHS data with bmi below 23 and age below 36 had been diagnosed with diabetes. according to that assumetion we can see the lowest diabetes