---
title: "STAT 184 Homework Exercises"
author: "zhiyaun zhang"
subtitle: DataComputing Chapters 8
output:
  html_document:
    df_print: paged
---

###question 10.1
##1 summaryfunction
##2 dataverb
##3 reductionfunction
##4 reductionfunction
##5 dataverb
##6 summaryfunction
##7 dataverb
##8 summaryfunction

###question 10.2
##1 mutate()
##2 arrange()
##3 filter()
##4 select()
##5 select()+group_by/()

## question 10.3
##1 nrow()
##2 names()
##3 help(),library(codebook)
##4 library()
##5 group_by()

## question 10.4
##1 Babynames %>% arrange(asc(count))
##2 Babynames %>% filter(sex == F)
##3 Babynames %>% filter(sex == M)
##4 Babynames %>% summarise(total =())
##5 Babynames %>% select(name, count)

##question 10.5
##1 1910
##2
##3
```{r}
library(mosaic)
library(dcData)
data(Minneapolis2013)
Minneapolis2013 %>%
  select(First, Second)%>%
  count(First == Second)
##Minneapolis2013 %>%
##select(First) %>%
##group_by(OLE_SAVIOR)%>%
##arrange(desc(total))
  
```

##question 10.6
##1
```{r}
library(tidyverse)
library(ggplot2)
diamonds %>%  group_by(color) %>% 
  summarise("mean" = sum(mean(carat))) %>% 
  arrange(desc(mean)) %>% 
  head(1)
```
##2
```{r}
diamonds %>%  group_by(clarity) %>% 
  summarise("mean" = sum(mean(table/carat))) %>% 
  arrange(desc(mean)) %>% 
  head(1)

```



### question10.7

##1
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(total = n()) %>%
  mutate(First = ifelse(total < 5000, "minor", First))

```
